---
title: "Cheat Sheet"
format: html
toc: TRUE
toc_float: TRUE
editor: visual
---

## VARIABLES

\- Assign a value to a variable using the \<- operator or the = sign

\- Variables can hold numbers, strings, or logical values (TRUE or FALSE)

```{r}
#| label: variables
x <- 5             # assign 5 to variable x

y <- "hello"       # assign "hello" to variable y

z <- TRUE          # assign TRUE to variable z
```

## DATA TYPES

\- Numeric: for numbers

\- Character: for text

\- Logical: for TRUE/FALSE values

```{r}
#| label: data_types

x <- 5             # numeric

y <- "hello"       # character

z <- TRUE          # logical
```

## VECTORS

\- A vector is a collection of values of the same data type

\- Create a vector using the c() function

```{r}
#| label: vectors
x <- c(1, 2, 3, 4)       # create a numeric vector

y <- c("red", "green", "blue") # create a character vector
```

## SUBSETTING

\- Access elements of a vector using the \[\] operator

\- Use a colon to select a range of values

```{r}
#| label: subsetting

x[1]                # get the first element of x

y[2:3]              # get the second and third elements of y
```

## CONDITIONALS

\- Use if-else statements to execute code based on a condition

\- Use comparison operators (\<, \>, \<=, \>=, ==, !=) to compare values

```{r}
#| label: conditionals
x <- runif(1, 0, 10)
if (x > 5) {

  print("x is greater than 5")

} else {

  print("x is less than or equal to 5")

}
```

## LOOPS

\- Use for loops to repeat a block of code a specified number of times

\- Use while loops to repeat a block of code as long as a condition is true

```{r}
# label: loops
for (i in 1:10) {

  print(i)

}
```

## FUNCTIONS

\- A function is a block of code that performs a specific task

\- Define a function using the function() keyword

```{r}
# label: functions
myFunction <- function(x, y) {

  return(x + y)

}
```

## Comprehensive Cheat Sheet

[Cheat sheet](https://iqss.github.io/dss-workshops/R/Rintro/base-r-cheat-sheet.pdf)
